Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-05-23 paper.tex
Added Sam Adams to author list; Fixed Daniel Lowe's affiliation
spelling (s/scafold/scaffold/)

Silicos has release several Open Source utilities based on
OpenBabel, such as Pharao, a tool for pharmacophore searching,
Sieve for filtering molecular structure by molecular property,
Stripper for removing core scafold structures from a molecule
set, and Piramid for molecular alignment using shape determined
by the Gaussian volumes as a descriptor. Additionally,
contributions have been made to the OpenBabel project itself.

>>>>

Silicos has release several Open Source utilities based on
OpenBabel, such as Pharao, a tool for pharmacophore searching,
Sieve for filtering molecular structure by molecular property,
Stripper for removing core scaffold structures from a molecule
set, and Piramid for molecular alignment using shape determined
by the Gaussian volumes as a descriptor. Additionally,
contributions have been made to the OpenBabel project itself.
